Risk Perceptions for Wearable Devices

### 2015-01-07 wearables_survey.tex
Spliced related work: Felt and Fischhoff in Methodology: Motivation (rough) and the rest of related work is after the Discussion section (also still rough).

\section{Related Work}
In this section, we discuss related work on emerging challenges related to ubiquitous computing, threats to smartphone users, and risk perceptions pertaining to technologies.

Among such studies, Felt \etal were among the first to examine the security concerns of smartphone users using a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Participants were asked how upset they would be if a certain action had occurred without their permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our work builds upon this study, by aiming to evaluate the types of concerns that users have surrounding future wearable device capabilities, and then to compare those concerns to concerns surrounding more established technologies.

%~\cite{laurier2001people}: Why people say where they are during mobile phone calls

\subsection{User Perceptions and Behaviors}

Fischhoff \etal performed a seminal technology risk perception experiment in which they studied how people perceived the risks and benefits of 30 common activities and technologies~\cite{Fischhoff}. In their study, participants were prompted to separately rate the risks and benefits of 30 activities and technologies. They were primed to think about all people affected by the technology, and to think about long-term vs. short-term risks and benefits. The participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (i.e. a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10). Using this mythology, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.

While user perceptions are insightful, it has been shown that people generally lack enough information to make privacy-sensitive decisions; even if they do, they are likely to trade off long-term privacy for short-term benefits ~\cite{acquisti2005privacy}. Actual behavior deviates from self-reported behaviors ~\cite{jensen2005privacy} and privacy preferences ~\cite{spiekermann2001privacy}.

%I'm not sure that having a background on crowdsourcing is relevant, especially given the space limitations. Instead, you need WAY more related work on ubiquitous privacy concerns, as well as smartphone privacy concerns. There's also probably more general work on risk perceptions that should probably be cited.

%\subsection{Crowdsourced User Studies}
%Crowdourcing user studies in Mechanical Turk has its challenges \cite{kittur2008crowdsourcing}. While the Amazon Mechanical Turk population is diverse across several significant demographic dimensions such as age, gender, and income, it is not a precise representation of the U.S. population \cite{ross2010crowdworkers}\cite{kelley2010conducting}. Additionally, Amazon Mechanical Turk workers generally put a higher value on anonymity and hiding information, were more likely to do so, had more privacy concerns than the larger U.S. public \cite{kang2014privacy}.

\section{Methodology}
Our survey consisted of multiple sections. In one section, we presented participants with scenarios surrounding a wearable device and asked them to rate their level of concern if each scenario were to happen. Next, we asked participants about similar scenarios, substituting smartphones for the wearable device in order to see whether participants' familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones). Following those questions, we asked participants to compare the risks and benefits of wearable technologies with better understood technologies. Finally, we collected demographic information, which included a privacy concern scale, and whether participants owned any wearable devices.

%%% commented out for anonymity; can comment back in later.
%The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.

@@

@@

%COMMENTED OUT FOR ANONYMITY!!

>>>>

\section{Methodology}
%David TODO: add sentence about the methodology motivation in the overview paragraph. 
Our survey consisted of multiple sections. In one section, we presented participants with scenarios surrounding a wearable device and asked them to rate their level of concern if each scenario were to happen. Next, we asked participants about similar scenarios, substituting smartphones for the wearable device in order to see whether participants' familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones). Following those questions, we asked participants to compare the risks and benefits of wearable technologies with better understood technologies. Finally, we collected demographic information, which included a privacy concern scale, and whether participants owned any wearable devices.

%LL: this commented out for anonymity; can comment back in later.
%%% The full survey can be found at http://www.surveygizmo.com/s3/1657924 /Wearables-Threats-User-Survey.

%::LL: David, I spliced the related work; the text related to work directly related to our research to introduce/motivate the methodology remains here. The rest were put at the end of the paper, as you requested.

\subsection{ROUGH: Methodology Motivation} %LL: this text was previously inside related work
{\color{red} Note: this section is a placeholder. Maybe we should put as a subsection inside the methodology section. TODO: reword so that these works seem not like related work, but as motivation for our methodology; i.e. ``here are two methodologies from relevant work swe chose to use for reasons.'' We can also say that we extend their works.}

\subsubsection{Smartphone User Concerns} %LL: this text was previously inside related work
Among such studies, Felt \etal were among the first to examine the security concerns of smartphone users using a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Participants were asked how upset they would be if a certain action had occurred without their permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our work builds upon this study, by aiming to evaluate the types of concerns that users have surrounding future wearable device capabilities, and then to compare those concerns to concerns surrounding more established technologies.

\subsubsection{Technology Risk Perception} %LL: this text was previously inside related work
Fischhoff \etal performed a seminal technology risk perception experiment in which they studied how people perceived the risks and benefits of 30 common activities and technologies~\cite{Fischhoff}. In their study, participants were prompted to separately rate the risks and benefits of 30 activities and technologies. They were primed to think about all people affected by the technology, and to think about long-term vs. short-term risks and benefits. The participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (i.e. a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10). Using this mythology, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.

@@

% LL: David, thanks for polishing up the related work!
%LL: Related work put at the end upon David's Suggestion. Paper flow is much better. 
\section{Related Work}
In this section, we discuss related work on emerging challenges related to ubiquitous computing, threats to smartphone users, and risk perceptions pertaining to technologies.

\subsection{User Perceptions and Behaviors}
While user perceptions are insightful, it has been shown that people generally lack enough information to make privacy-sensitive decisions; even if they do, they are likely to trade off long-term privacy for short-term benefits ~\cite{acquisti2005privacy}. Actual behavior deviates from self-reported behaviors ~\cite{jensen2005privacy} and privacy preferences ~\cite{spiekermann2001privacy}.

@@

%NOTE: RESEARCH ETHICS/ ACKS COMMENTED OUT FOR ANONYMITY
